---
title: "Example Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(here)
library(tidyverse)
```

```{r}

if(!dir.exists("../data")){
  dir.create("../data")
}


if(!file.exists(here("../data", "scoobydoo.RDS"))){
  tuesdata <- tidytuesdayR::tt_load('2021-07-13')
  tuesdata <- tidytuesdayR::tt_load(2021, week = 29)
  
  scoobydoo <- tuesdata$scoobydoo
  
  saveRDS(scoobydoo, file=here("../data","scoobydoo.RDS"))
}

```

# Data
Data is from Scooby Doo TV series found in TidyTuesday along with its data dictionary: https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md

```{r, warning=FALSE}
scoobydoo <- readRDS(here("../data", "scoobydoo.RDS"))


scoobydoo_long = scoobydoo %>%
  mutate(across(starts_with("caught_"), as.logical),
         across(starts_with("captured"), as.logical)) %>% 
  pivot_longer(cols = starts_with("caught_"),
               names_to = "caught_by",
               values_to = "caught_value") %>% 
  pivot_longer(cols = starts_with("captured_"),
               names_to = "captured_by",
               values_to = "captured_value") %>% 
  mutate(captured_by=str_remove(captured_by, "captured_"))


```


# Question: Is there a difference in IMDB rating across seasons? 

```{r, warning=FALSE}
scoobydoo_long$imdb=as.numeric(scoobydoo_long$imdb)


scoobydoo_long %>% 
  filter(season==c(1, 2, 3, 4)) %>% 
  ggplot(aes(x=imdb, color=`season`)) +
  geom_density() +
  labs(title="Distribution of IMDB rating across Scooby Doo seasons",
       subtitle=str_wrap("Season 3 of Scooby Doo on average has higher ratings"),
       x="IMDB rating",
       y="Density")

```

# Question: What is the correlation between number of monsters in a Scooby Doo episode and IMDB rating?

```{r, warning=FALSE}
scoobydoo_long %>%
  filter(season %in% c(1, 2, 3, 4)) %>% 
  ggplot(aes(x = monster_amount, y = imdb)) + 
  geom_point() + geom_smooth() +
  labs(title="Correlation between number of monsters in a Scooby Doo episode and IMDB rating",
       subtitle=str_wrap("An increase in monsters in an episode is associated with lower ratings"),
       x="Number of monsters in a single episode",
       y="IMDB rating")
  
```

# Question: What is the average IMDB rating when different Scooby Doo characters catch the monsters?
```{r, warning=FALSE}

summary_table <- scoobydoo_long %>%
  filter(season %in% c(1, 2, 3, 4),
         is.na(captured_value)==FALSE) %>% 
  group_by(season, captured_by, captured_value) %>%
  summarize(avg_imdb = mean(imdb, na.rm = TRUE)) 
  

# Assuming your summary_table is named summary_table
ggplot(summary_table, aes(x = captured_by, y = avg_imdb, fill = captured_value)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  facet_wrap(~season, scales = "free_y", ncol = 2) +
  labs(title = "Average IMDB Rating when monster is caught by different Scooby Doo character",
       subtitle = str_wrap("The Scooby Doo character who captures the monster does not seem to affect the IMDB rating of the season"),
       x = "Character ",
       y = "Average IMDB Rating") 

```

# Results and Interpretation
It does not seem to make a huge difference which Scooby Doo character captures the monster. Moreover, there is a negative association between IMDB ratings and # of monsters in an episode. Season 3 seems to have overall better ratings than the other seasons.
